A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Updates from Overleaf

\begin{figure}[h!]
    \centering
    \pgfplotsset{}
    % \inputtikz{figures/anal_sim_comp/anal_sim_comp}
    \includegraphics{figures/anal_sim_comp/anal_sim_comp}
    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).}
    \label{fig: anal_sim_comp}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \pgfplotsset{}
    % \inputtikz{figures/anal_sim_comp/anal_sim_comp}
    \includegraphics[height=9cm]{figures/anal_sim_comp/anal_sim_comp.pdf}
    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).  (a) is the nullcline for the FitzHugh-Nagumo (simulated) equations, (b) is the "head oscillator" simulated (two neurons which mutually inhibit each other), (c) is the "descending pathway" simulated (one neuron driving another).  (d) is the nullcline for the analog circuit - a piecewise linear approximation to the cubic, (e) is the analog version of the head oscillator, and (f) is the analog version of the descending pathway.}
    \label{fig: anal_sim_comp}
\end{figure}
